\documentclass[11pt,a4paper,sans]{moderncv}

% ModernCV theme
\moderncvstyle{banking}
\moderncvcolor{blue}

% Character encoding
\usepackage[utf8]{inputenc}

% Adjust page margins
\usepackage[scale=0.85]{geometry}

% Personal data
\name{Ruslan}{Palchuk}
\title{Data Scientist}
\address{Kyiv, Ukraine}{}{}
\email{ruslanpalchuk@gmail.com}
\social[linkedin]{ruslan-palchuk-116464168}
\social[github]{LeoRuslan}
\homepage{iamreader.com.ua}

% Photo (optional)
% \photo[64pt][0.4pt]{photo}

\begin{document}

\makecvtitle

\section{Summary}
Experienced Data Scientist with a strong mathematical background (Master's in Mathematics) and over 6 years of expertise in Machine Learning. My primary focus is Research \& Development, investigating complex algorithms for \textbf{Time-Series Forecasting} and \textbf{Speech Recognition}. I combine technical research with mentorship, guiding interns in data science methodologies. Passionate about data visualization and building analytical tools.

\section{Work experience}

\cventry{Jan 2019 -- Present}{Data Scientist}{SoftElegance (a-Gnostics)}{}{}{
\textit{Domain: Energy Consumption \& Generation Forecasting}\\[0.2cm]
\textbf{Responsibilities:}
\begin{itemize}
\item \textbf{Research \& Modeling:} Conducting deep research and implementing ML models for forecasting electricity and gas consumption/generation.
\item \textbf{High Accuracy:} Successfully achieved >98\% accuracy for specific locations through advanced time-series analysis techniques.
\item \textbf{Algorithm Development:} Developing and validating custom algorithms for processing and validating time-series data.
\item \textbf{Mentorship:} Mentoring interns, supervising their research tasks, and conducting code reviews to ensure best practices in Data Science.
\end{itemize}
\textbf{Technologies:} Python, Time-Series Analysis, Machine Learning, Keras, PostgreSQL
}

\vspace{0.2cm}
{\color{gray}\hrule height 0.3pt}
\vspace{0.3cm}

\cventry{Mar 2023 -- Present}{Data Scientist (Speech Recognition)}{eKidz.eu}{}{}{
\textit{Domain: EdTech, Language Learning for Children}\\[0.2cm]
\textbf{Responsibilities:}
\begin{itemize}
\item \textbf{Speech Research:} Researching and implementing Automatic Speech Recognition (ASR) solutions specifically tailored for children's speech patterns and acoustics.
\item \textbf{Integration:} Connecting and evaluating various ASR providers to optimize word and phoneme recognition accuracy.
\end{itemize}
\textbf{Technologies:} Python, Azure Speech Recognizer, VOSK, WhisperX
}

\vspace{0.2cm}
{\color{gray}\hrule height 0.3pt}
\vspace{0.3cm}

\cventry{Sep 2013 -- Present}{Math Tutor}{Private Practice}{}{}{
\textbf{Responsibilities:}
\begin{itemize}
\item Preparing students for the External Independent Evaluation (ZNO/NMT).
\item Improving knowledge and problem-solving skills in mathematics.
\end{itemize}
}

\section{Projects}

\cventry{}{IamReader}{\href{https://iamreader.com.ua}{iamreader.com.ua}}{}{}{
A data visualization tool created by a reader for readers to analyze personal reading habits over the years.
\begin{itemize}
\item Developed interactive charts to track reading statistics (book vs. page counts).
\item Customizable design themes and report generation features.
\item Provides a "bigger picture" of reading analytics beyond standard yearly reviews.
\end{itemize}
}

\section{Skills}

\cvitem{Core}{Data Science Research, Mathematical Modeling, Algorithms, Mentoring}
\cvitem{Domains}{Time-Series Forecasting, Computer Vision (OCR), Automatic Speech Recognition}
\cvitem{Languages \& Libraries}{Python, Pandas, NumPy, SciPy, Scikit-learn, SQL}
\cvitem{ML \& AI}{Keras, XGBoost, ARIMA, Azure Speech Services, VOSK, WhisperX}
\cvitem{Visualization}{Tableau, Matplotlib, Seaborn, Plotly}
\cvitem{Tools}{Git, Ubuntu, LaTeX, PyCharm, GitHub}

\section{Languages}
\cvitemwithcomment{Ukrainian}{Native}{}
\cvitemwithcomment{English}{Intermediate}{}і

\section{Education}
\cventry{2011 -- 2017}{Master's Degree in Mathematics (Honors)}{Taras Shevchenko National University of Kyiv}{}{}{
\href{https://mechmat.knu.ua/}{Faculty of Mechanics and Mathematics}\\
Specialty: Algebra and Basics for Data Protection
}

\section{Awards \& Achievements}
\cvlistitem{\textbf{2010:} Certificate of Thanks from the President of Ukraine and a nominal clock for high achievement in education.}
\cvlistitem{\textbf{2009--2010:} Winner of the Minor Academy of Sciences of Ukraine (3rd place, Applied Mathematics section).}
\cvlistitem{\textbf{2007, 2010:} Winner of the Regional Mathematics Olympiad (2nd and 3rd places).}

\end{document}
